\documentclass[ignorenonframetext]{beamer}
\usetheme{Madrid}
\usepackage[utf8x]{inputenc}
\usepackage{bortzmeyer-utils}

\title{NXDOMAIN cut, next steps}
\author{Stéphane Bortzmeyer - AFNIC \& Shumon Huque - Verisign Labs}
\date{IETF 95 - Buenos Aires - dnsop WG}

\begin{document}

\begin{frame}
\maketitle  
\end{frame}

\begin{frame}
  \frametitle{Recent news}
  \begin{itemize}
  \item<2->Lots of discussion before the adoption by the WG
  \item<3->Draft -00 published in december 2015
  \item<4->Everything quiet after that
  \item<5->Two implementations discovered (Unbound and PowerDNS)
  \item<6->Draft -01 published in march 2016, generating 105 messages
    on the list
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Lasting issues}
  \begin{enumerate}
  \item<1->The idea is to \emph{recommend} a behaviour, without
    requiring (SHOULD, not MUST, not MAY)
  \item<2->Too much ``implementation-oriented''? Domain names
    \emph{are a tree}. It's a model, not an implementation. Text to
    add for -02
  \item<3->''Security'' issue with cache poisoning. Can I delete
    the whole \url{.com} with a successful packet? Limit NXDOMAIN cut to
    DNSSEC like Unbound does? MAY? Possible reference to \path{draft-fujiwara-dnsop-nsec-aggressiveuse}?
   \item<4->Can a resolver send cached responses under the NXDOMAIN
     cut? ``Eventual consistency''? (It was for ≠ servers.) SHOULD?
     Not explicit in -01
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Way forward}
  \begin{enumerate}
  \item<2->Document is ready after -02 will be published?
  \item<3->Or is there a big unsolved problem?
  \end{enumerate}
\end{frame}

\end{document}
